Spatiotemporal models of `r paste(params$species)` biomass with climate covariates

### 2019-12-17 analysis/VOCC/2-biomass-depth-only-model.Rmd
add model assessment plots for depth only and dixed depth climate model building

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Redbanded Rockfish"
    region: "All synoptic surveys"
    knots: 600
    covariates: "+trawled+as.factor(ssid) + trawled:as.factor(ssid)" # additional fixed-effect covariates
    covs: "-trawled-ssid-reml" # covariate string used to name model rds 
    update_model: TRUE
---

@@

>>>>

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    #species: "Redbanded Rockfish"
    #species: "Pacific Ocean Perch"
    species: "Pacific Cod"
    #species: "Petrale Sole"
    region: "All synoptic surveys"
    knots: 800
    covariates: "+trawled+as.factor(ssid) + trawled:as.factor(ssid)" 
    # additional fixed-effect covariates
    covs: "-trawled-ssid-reml" # covariate string used to name model rds 
    update_model: TRUE
---

@@

```{r}
adult_biomass <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"))

point_predictions <- predict(adult_biomass)
point_predictions$residuals <- residuals(adult_biomass)

saveRDS(point_predictions, file = paste0("data/", spp,
    "/check-mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"))

```

```{r}
depth_only_predictions <- readRDS(paste0("data/", spp,
    "/check-mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"))

depth_only_predictions <- filter(depth_only_predictions, ssid %in% c(1,3)) %>% filter (year > 2007)

ggplot(depth_only_predictions, aes(adult_density, residuals, colour = adult_density)) + 
  geom_point() + scale_x_continuous(trans = 'log10') + facet_wrap(~year)
```

```{r}
ggplot(depth_only_predictions, aes((est), residuals, colour = adult_density)) +
  geom_point() + 
  #scale_x_continuous(trans = 'log10') + 
  facet_wrap(~year)
```

```{r}
ggplot(depth_only_predictions, aes(X, Y, colour = (residuals))) + 
  geom_point() + 
  scale_colour_gradient2() + 
  scale_x_continuous(trans = 'log10') + 
  facet_wrap(~year) 
```

### 2019-12-17 analysis/VOCC/3-climate-models-fixed-depth.Rmd
add model assessment plots for depth only and dixed depth climate model building

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with climate covariates"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    #species: "Redbanded Rockfish"
    #species: "Pacific Cod"
    #species: "Pacific Ocean Perch"
    #species: "Arrowtooth Flounder" #all DO smiley
    #species: "Petrale Sole" #adult DO almost quadratic...
    #species: "English Sole" #all DO smiley
    #species: "Dover Sole" #all DO smiley
    species: "Flathead Sole"
    region: "All synoptic surveys"
    #region: "Both odd year surveys"
    log_temp: TRUE # should temperature be log()
    model_w_do: TRUE
    priors: FALSE
    knots: 600
    # knots: 500
    covariates: "+trawled" # additional non-climate variables #+as.factor(ssid)
    covs: "-past" # hardcoded "-fixed" makes covs = "-fixed-past"
    year_cutoff: 2013
    # covs: "-all" # hardcoded -fixed makes covs = "-fixed-all"
    # year_cutoff: NULL
    #"-log-both-fixed-depth" #"-log-both-noAR1" # string describing model covariates
---

@@

# d <- data %>% filter(year==2011) #%>% filter(depth> 400) 
# = plot((adult_density)~(depth), data=d)
if (covs == "-past") data <- filter(data, year < year_cutoff)
```

@@

>>>>

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with climate covariates"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    #species: "Redbanded Rockfish"
    #species: "Pacific Cod"
    #species: "Pacific Ocean Perch"
    #species: "Arrowtooth Flounder" #all DO smiley
    species: "Petrale Sole" #adult DO almost quadratic...
    #species: "English Sole" #all DO smiley
    #species: "Dover Sole" #all DO smiley
    #species: "Flathead Sole"
    region: "All synoptic surveys"
    log_temp: TRUE # should temperature be log()
    model_w_do: TRUE
    priors: FALSE
    knots: 600
    #knots: 500
    covariates: "+trawled" # additional non-climate variables #+as.factor(ssid)
    covs: "-past" # hardcoded "-fixed" makes covs = "-fixed-past"
    year_cutoff: 2015
    #covs: "-all" # hardcoded -fixed makes covs = "-fixed-all"
    #year_cutoff: NULL
    #"-log-both-fixed-depth" #"-log-both-noAR1" # string describing model covariates
---

@@

# d <- data %>% filter(year==2011) #%>% filter(depth> 400) 
# = plot((adult_density)~(depth), data=d)
if (covs == "-past") data <- filter(data, year < year_cutoff)

 # saveRDS(data, file = paste0(spp, "-with-covariates-all-years.rds"))
 # glimpse(data)
```

@@

```{r}
adult_biomass <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-fixed", covs, "-", year_cutoff, "-", ssid_string, "-prior-", priors, ".rds"
        ))

point_predictions <- predict(adult_biomass)
point_predictions$residuals <- residuals(adult_biomass)

saveRDS(point_predictions, file = paste0("data/", spp,
    "/check-mod-mat-biomass-", spp, "-fixed", covs, year_cutoff, "-", ssid_string, "-prior-", priors, ".rds"))
```

```{r}
all_fixed_predictions <- readRDS(paste0("data/", spp,
    "/check-mod-mat-biomass-", spp, "-fixed", covs, year_cutoff, "-", ssid_string, "-prior-", priors, ".rds"))

all_fixed_predictions <- filter(all_fixed_predictions, ssid %in% c(1,3))

ggplot(all_fixed_predictions, aes(adult_density, residuals)) + 
  geom_point() + scale_x_continuous(trans = 'log10') + facet_wrap(~year)
```

```{r}
ggplot(all_fixed_predictions, aes(est, residuals, colour = adult_density)) + 
  geom_point() + 
  #scale_x_continuous(trans = 'log10') + 
  facet_wrap(~year)
```

```{r}

ggplot(all_fixed_predictions, aes(X, Y,  colour = residuals)) + 
  geom_point() + 
  scale_colour_gradient2() + 
  scale_x_continuous(trans = 'log10') + 
  facet_wrap(~year) 
```
